### 2019-12-13 README.Rmd
Update names with sd commands

```{r}
library(sf)
devtools::load_all()
plot(sq_study_region)
```

@@

```{r}
x = sq_study_region
q = sq_quadrat(x, 4) # break into 4
plot(q)
```

@@

```{r}
plot(sq_dohnut(x, n = 4))
dohnut_4km = sq_dohnut(x, d = 4)
dohnut_4km
plot(sf::st_geometry(dohnut_4km))
plot(dohnut_4km[3, ], col = "blue", add = TRUE)
```

>>>>

```{r}
library(sf)
devtools::load_all()
plot(sz_study_region)
```

@@

```{r}
x = sz_study_region
q = sz_quadrat(x, 4) # break into 4
plot(q)
```

@@

```{r}
plot(sz_dohnut(x, n = 4))
dohnut_4km = sz_dohnut(x, d = 4)
dohnut_4km
plot(sf::st_geometry(dohnut_4km))
plot(dohnut_4km[3, ], col = "blue", add = TRUE)
```
